Reasoning About a Machine with Local Capabilities

### 2019-08-20 toplas/paper.tex
typo and comment in TODO file

\begin{toplas}
  Intuitively, the future world relation specifies how memory protocols may change over time.
  Rather than deleting regions in future worlds, we follow the approach in \citet{Thamsborg:2011:KLR:2034773.2034831,Ahmed2004semantics} and use masks to signal which regions are active.
  This approach implies that the future world relation is a preorder and hence we can use the
  method in \citet{Birkedal:2011:SKM:1926385.1926401,Birkedal:tutorial-notes} to solve the recursive world equation.
\end{toplas}

@@

\begin{toplas}
  \emph{Why use a logical relation and not a simpler proof technique?}
  The concept of a capability exists on different levels of abstraction on computers, so capabilities have been studied and safety properties proven about them in other contexts than assembly languages.
  Traditionally, logical relations have not been used for safety property proofs, so why do we need one here?
  To answer this question let's compare this work to \citet{sewel_integrity_2011} where they prove \textit{integrity} and \textit{authority confinement} for the seL4 Microkernel.
  % Describe what they prove
  The security properties they show are relative to a security policy that specifies the upperbound of capabilities a subject in the system can posses.
  The security policy is expressed as a collection of possible capabilities in the system, e.g.\ \textit{subject A can have a write capability for memory B.}
  However, their policy are, in a sense, binary: subject A is either allowed to write to memory B or not.
  If writing is allowed, then any value can be written, as long as that value is itself legal.
  \citet{sewel_integrity_2011}'s results are not parametrised by a (possibly more restrictive) policy that subject A should observe on memory B.
  Our approach is much more fine-grained and allows us to define, for example, a policy that subject A can write to memory B, but only if the value is an even number.
  Because our invariants are indexed by worlds themselves, we can even define a policy that capabilities written to memory B must respect certain other invariants themselves.
  It is exactly the expressive invariants that enable us to prove the awkward example.
  We place a protocol on the memory where variable \texttt{x} is stored that says that it sometimes can be either $0$ or $1$ and at other times it has to be $1$.

>>>>

\begin{toplas}
  In order to be able to solve the recursive domain equation, we want the future world relations to be extensional.
  Intuitively, the future world relation specifies how memory protocols may change over time.
  If the future world relation was not extensional, then the protocols could just disappear entirely regardless of what they promise.
  A piece of memory can still be repurposed under the right circumstances, i.e., if the protocol allows it under the future world relation used.
  In practice, the extensionality of future worlds means that a future world cannot forget about region names in a past world.
  This is the reason we use masks rather than deleting the regions altogether.
  It does not, however, matter what kind of region is used as a mask; it is the region name we must retain.
  This is why we allow revoked regions to be replaced by other regions in the two future world relations.
  This may seem unnecessary as the future world relation allows new regions to be added.
  However, for technical reasons in private future worlds, we need to be able to reinstate old regions with the same region names as they had in a past world.
  Further, we do not want public future worlds to be able to prevent reinstation in private future worlds.
  Private future worlds cannot revoke permanent regions, so we cannot allow public future worlds to use permanent regions as masks for revoked regions.
\end{toplas}

@@

\begin{toplas}
  \emph{Why use a logical relation and not a simpler proof technique?}
  The concept of a capability exists on different levels of abstraction on computers, so capabilities have been studied and safety properties proven about them in other contexts than assembly languages.
  Traditionally, logical relations have not been used for safety property proofs, so why do we need one here?
  To answer this question let's compare this work to \citet{sewel_integrity_2011} where they prove \textit{integrity} and \textit{authority confinement} for the seL4 Microkernel.
  % Describe what they prove
  The security properties they show are relative to a security policy that specifies the upperbound of capabilities a subject in the system can posses.
  The security policy is expressed as a collection of possible capabilities in the system, e.g.\ \textit{subject A can have a write capability for memory B.}
  However, their policies are, in a sense, binary: subject A can either not write or write anything to memory B.
  Our approach is much more fine-grained and allows us to define, for example, a policy that subject A can write to memory B, but only if the value is an even number.
  Because our invariants are indexed by worlds themselves, we can even define a policy that capabilities written to memory B must respect certain other invariants themselves.
  It is exactly the expressive invariants that enable us to prove the awkward example.
  We place a protocol on the memory where variable \texttt{x} is stored that says that it sometimes can be either $0$ or $1$ and at other times it has to be $1$.
